Tips for Writing a Research Paper using \LaTeX

### 2021-11-19 paper_writing_tips.tex
Fix minors

In this article, we will first provide some tips for paper writing.  
using \LaTeX. 
Then, we will showcase several working examples for the table and figure, which have been used in my previous publications. The readers are encouraged to adapt those tables and figures to their purposes to save time.

@@

% two column
\input{tables/table8} % two-column table
\input{tables/table12} % two-column table with remarks
\input{tables/table9} % two-column table with color header
\input{tables/table7} % two-column table with two sub-tables
\input{tables/table_figure2} % two-column tables with images in the header
\input{tables/table10} % two tables side-by-side
\input{tables/table11} % table with caption at the left

@@

% Two column
\input{figures/figure7} % single image
\input{figures/figure8} % multiple images
\input{figures/figure9} % multiple images with two zoom in patches (horizontal)
\input{figures/figure11} % multiple images with two zoom in patches (vertical) 
\input{figures/figure13} % two figure placed side-by-side
\input{figures/figure12} % figure with caption at the left
\input{figures/figure14} % figure numeric results and color bar

\input{figures/figure10} % multiple images organized with multi-level

>>>>

In this article, we will first provide some tips for paper writing.  
Then, we will showcase several working examples for the tables and figures, which have been used in our previous publications. The readers are encouraged to adapt those tables and figures to their purposes to save time when preparing their first papers.

@@

% two column
\input{tables/table8} % two-column table
\input{tables/table12} % two-column table with remarks
\input{tables/table9} % two-column table with color header
\input{tables/table7} % two-column table with two sub-tables
\input{tables/table_figure2} % two-column tables with images in the header
\input{tables/table10} % two tables side-by-side

\clearpage
\input{tables/table11} % table with caption at the left

@@

% Two column
\input{figures/figure7} % single image
\input{figures/figure8} % multiple images
\input{figures/figure9} % multiple images with two zoom in patches (horizontal)
\input{figures/figure11} % multiple images with two zoom in patches (vertical) 
\input{figures/figure13} % two figure placed side-by-side
\input{figures/figure12} % figure with caption at the left
\input{figures/figure14} % figure numeric results and color bar
\input{figures/figure10} % multiple images organized with multi-level
